Thesis Title

### 2022-03-21 coverpage.tex
update
add new FCT reference

@@

        \Huge
        {Towards accreditation in metagenomics \\[1ex] for clinical microbiology}
        \normalsize

        Catarina Inês Marques de Sousa Mendes

@@

@@

        Fundação para a Ciência e Tecnologia SFRH/BD/129483/2017

        2022

    \end{center}
\end{titlepage}

>>>>

        \vspace{1cm}

@@

        \vspace{1cm}

        \huge
        \textbf{Towards accreditation in metagenomics \\[1ex] for clinical microbiology}
        \normalsize

        \vspace{0.8cm}

        \large
        Catarina Inês Marques de Sousa Mendes
        \normalsize

        \vspace{0.8cm}

@@

        \vspace{0.8cm}

@@

        Fundação para a Ciência e Tecnologia \\ 
        SFRH/BD/129483/2017 and COVID/BD/152583/2022

        \vspace{0.2cm}

        2022
    \end{center}
\end{titlepage}
